Global patterns of forest autotrophic carbon fluxes

### 2020-01-20 manuscript/manuscript draft.Rmd
worked on growing season results

*Within the growing season, how does FACF vary with climate?* When FACF was standardized by growing season length, correlations with climate variables were much weaker. Temperature, precipitation, PET, and solar radiation each had a small effect on one or more FACF (Fig. **S#**). Specifically, there was a small increase in productivity with temperature and precipitation for ANPP (with temperature $R^2$ = 0.10, p<0.001; with precipitation $R^2$ = 0.04, p<0.05) and ANPP~foliage~ (with temperature $R^2$ = 0.16, p<0.01; with precipitation $R^2$ = 0.09, p<0.05). Productivity increased with solar radiation for GPP ($R^2$ = 0.21, p<0.001), NPP ($R^2$ = 0.21, p<0.001), BNPP ($R^2$ = 0.16, p<0.001) and BNPP~fine~ ~root~ ($R^2$ = 0.12, p<0.01), and with PET for GPP ($R^2$ = 0.15, p<0.01), NPP ($R^2$ = 0.18, p<0.01), BNPP ($R^2$ = 0.23, p<0.0001), BNPP~fine~ ~root~ ($R^2$ = 0.11, p<0.05), and ANPP~woody~ ~stem~ ($R^2$ = 0.06, p<0.05).  {**site SI figure, stats might work better in a table**}  {**did we look at respiration in this anlaysis?**}

>>>>

*Within the growing season, how does FACF vary with climate?* When FACF was standardized by growing season length, correlations with climate variables were much weaker. Growing season temperature, precipitation, solar radiation, and PET each had a small effect on one or more of the nine FACF analyzed (Table 2; Fig. **S#**). Speficifally, $ANPP$ increased with growing season temperature ($R^2$ = 0.10, p<0.001) and precipitation ($R^2$ = 0.04, p<0.05). Similaryly, $ANPP_{foliage}$ increased slightly with growing season temperature ($R^2$ = 0.16, p<0.01) and precipitation ($R^2$ = 0.09, p<0.05). Growing season solar radiation had a positive influence on $GPP$ ($R^2$ = 0.21, p<0.001), $NPP$ ($R^2$ = 0.21, p<0.001), $BNPP$ ($R^2$ = 0.16, p<0.001) and $BNPP_{fine.root}$ ($R^2$ = 0.12, p<0.01). Growing season PET had a positive influence on $GPP$ ($R^2$ = 0.15, p<0.01), $NPP$ ($R^2$ = 0.18, p<0.01), $BNPP$ ($R^2$ = 0.23, p<0.0001), $BNPP_{fine.root}$ ($R^2$ = 0.11, p<0.05), and $ANPP_{woody-stem}$ ($R^2$ = 0.06, p<0.05). {**Becky, please verify/ edit the following:** There were no other signifcant correlations between growing season length-standardized FACF (9 variables in Table 2) and growing season climate (**which variables?**)}.
